Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-07 doc/report/discussion.tex
added some discussion

\textcolor{red}{Discuss the problems we have encountered and other random stuffs in this section.}

@@

>>>>

% Discuss the problems we have encountered and other random stuffs in this section
In this section, we will touch something that is related to our project, or pops up during our thinking that might be beneficial to people who consider working on similar topics. We will first talk about the attention-based interaction and its limitation. Then specific to our project implementation, we would like to express some of our experience.

@@

{\color{red} a very short brainstorming would be able to finish this part.}

\subsection{Experience learned in this project}
\label{sec:exper-learn-this}

XBee setting up.
